A Case For Multi-Objective Search In Automated Program Repair

### 2016-12-03 doc/final/manuscript.tex
Makefile Commit

			 Automated Patch generation has garnered a lot of attention in the past decade. It has long been a elusive goal in software engineering. Automation has been a key research area and yet debugging/patch generation remains a largely manual process. One success story in this endeavor is \textit{GenProg}. In fact, GenProg, widely accepted as a promising tool by the research community, is now used as a baseline to compare other new techniques. Albeit popular, there is a general lack of consensus on the need for such complex tools to generate effective patches. While some researchers opine that GenProg is quite effective in generating patches, given the existence of test cases, others disagree. They say that it is quite unclear if the efficacy of GenProg is merely due to its ``mutate'' operator or due to genetic programming. In this report we set out to these hypothesis. We conjectured that GenProg would be just as efficient if the core search strategy i.e., genetic programming, is replaced by other variants of genetic algorithms. In specific, we used NSGA-II, a very popular variant of genetic algorithm that has been extensively used and studied in search based software engineering. In addition to this, we also hypothesized that it is possible to generate better patches by converting genetic programming from it's current single objective form to a multiobjective search. Our findings contradict researchers claims that the success of genprog is the ``mutate'' operation. We show that genetic programming plays a critical role in the success of GenProg. Additionally, we show that by increasing the number of objectives used in fitness evaluation form one to two, GenProg succeeds in producing valid patches while also performing a more expansive search.\\
%       \newpage
			 \noindent{\bf Categories/Subject Descriptors:} D.2 [Software Engineering]; I.2
        [Artificial Intelligence];
	     \keywords{Defect Prediction; Data Mining; Transfer learning}
     \end{abstract}  		
\section{Introduction}

Maintaining released software is a rather difficult, time- consuming, and a manual
process. In their book, Seacord et al.~\cite{seacord:2003:MLS:599767} place software maintenance, traditionally defined as any modification made on a system after its delivery, at 90\% of the total cost of a typical software project. The literature on software maintenance is expansive. They all note that modifying existing code consumes a significant amount of maintenance effort. Anvik et al.~\cite{anvik2005coping} find that the number of outstanding software defects usually outnumbers the available resources to address them. Similarly, Liblit et al.~\cite{liblit2003bug} remark that several software systems are shipped to known and unknown bugs because of the lack of resources.

To alleviate the load on developers working on these issues automated patch generation has been proposed. Over the past decade research on this front has gained a lot of traction in the software engineering community. Specifically, tools that leverage evolution computation strategies, like GenProg~\cite{leGoues12}, have seen tremendous amounts of success.

@@

A motivation for this study was our hypothesis that the lack of efficiency of GenProg, in some cases, in this area is not due to the failure of Genetic Algorithms (or any evolutionary computation scheme for that matter), but due to incorrect and perhaps even incomplete modeling of the search space. We therefore propose the use of multiobjective search in automated program repair which extends the original single objective GenProg by adding additional objectives to satisfy the fitness function. Additionally, to verify if the success of GenProg is indeed due to genetic programming and not mutation/crossover operations, we study to performance of NGSAII~\cite{nsgaii}. It is also worth noting that, to be best of our knowledge, this is the first attempt to study multiobjective patch generation in automated program repair.

@@

\section{Research Questions}
\label{rq}
We conjecture that one way to further the research in the area of automated patch generation may be by modeling the domain as a multiobjective search problem. Consider genetic programming --- the algorithm works by trying to maximize the ``fitness'' score. In this case, the number of passing test cases given a patch. Algorithms like RSRepair, on the other hand, considers either repair effectiveness (as measured by the number patch trials required) or repair efficiency (measured by the number of test case executions). It not hard to see that each of these objectives namely, the number of passing test cases, the repair effectiveness, and the repair efficiency, are all important. Perhaps some are more important than others, but they all play a crucial role nonetheless.

@@

\subsection*{RQ3: Can we replace genetic programming by some other genetic algorithm?}
\label{rq3}
Assuming that we can answer RQ2, this question would be a natural extension to that. Here we ask what would happen if we used a different multiobjective optimizer in place of genetic programing. With this, we seek to validate (or perhaps deprecate) certain claims of studies by Qi et al.~\cite{qi2014}. They consider that the success of GenProg is due to the ``mutate'' operation of evolutionary algorithms and not genetic programming.

@@

We believe this to be untrue and to verify our opinion we replace GP with NSGAII~\cite{nsgaii}. NSGAII is a incredibly popular variant of GA (18000+ citations). NSGAII consists of a novel sort algorithm that enables it identify better solutions and to converge at these solution much faster.

@@

This measure is used to study the nature of patches generated by a search algorithm. It is entirely possible that a bug may be fixed in more that one way. Then, an method that can explore a much larger search space would be an enticing alternative to a narrow search scheme.  
\input{figs/results2.tex}
\section{Experimental Results}
\label{results}

@@

As for future work, efforts must be taken to update the notation of patches prior to performing search. Also, other novel search strategies that use both GP and Non-dominated sort may be explored. In addition to this, the usefulness of a promising new algorithm called SWAY\footnote{This algorithm is in current development by our research group}~\cite{chen2016sampling, nair2016accidental} may be also be investigated.

\bibliographystyle{unsrt}
\bibliography{references}
\end{document}

>>>>

			 Automated Patch generation has garnered a lot of attention in the past decade. It has long been an elusive goal in software engineering. Automation has been a key research area and yet debugging/patch generation remains a largely manual process. One success story in this endeavor is \textit{GenProg}. In fact, GenProg, widely accepted as a promising tool by the research community, is now used as a baseline to compare other new techniques. Albeit popular, there is a general lack of consensus on the need for such complex tools to generate effective patches. While some researchers opine that GenProg is quite effective in generating patches, given the existence of test cases, others disagree. They say that it is quite unclear if the efficacy of GenProg is merely due to its ``mutate'' operator or due to genetic programming. In this report we set out to these hypothesis. We tried to study if GenProg would be just as efficient if the core search strategy i.e., genetic programming, is replaced by other variants of genetic algorithms. In specific, we used NSGA-II, a very popular variant of genetic algorithm that has been extensively used and studied in search based software engineering. In addition to this, we also hypothesized that it is possible to generate better patches by converting genetic programming from it's current single objective form to a multiobjective search. Our findings contradict researchers claims that the success of genprog is the ``mutate'' operation. We show that genetic programming plays a critical role in the success of GenProg. Additionally, we show that by increasing the number of objectives used in fitness evaluation form one to two, GenProg succeeds in producing valid patches while also performing a more expansive search.\\
%       \newpage
			 \noindent{\bf Categories/Subject Descriptors:} D.2 [Software Engineering]; I.2
        [Artificial Intelligence];
	     \keywords{Defect Prediction; Data Mining; Transfer learning}
     \end{abstract}  		
\section{Introduction}

Maintaining released software is a rather difficult, time-consuming, and a manual
process. In their book, Seacord et al.~\cite{seacord:2003:MLS:599767} place software maintenance, traditionally defined as any modification made on a system after its delivery, at 90\% of the total cost of a typical software project. The literature on software maintenance is expansive. They all note that modifying existing code consumes a significant amount of maintenance effort. Anvik et al.~\cite{anvik2005coping} find that the number of outstanding software defects usually outnumbers the available resources to address them. Similarly, Liblit et al.~\cite{liblit2003bug} remark that several software systems are shipped with known ()and unknown) bugs because of the lack of resources.

To alleviate the load on developers working on these issues automated patch generation has been proposed. Over the past decade research on this front has gained a lot of traction within the software engineering community. Specifically, tools that leverage evolutionary computation strategies, like GenProg~\cite{leGoues12}, have seen tremendous amounts of success.

@@

A motivation for this study was our hypothesis that the lack of efficiency of GenProg, in some cases, is not due to the failure of Genetic Algorithms (or any evolutionary computation scheme for that matter), but due to incorrect and perhaps even incomplete modeling of the search space. We therefore propose the use of multiobjective search in automated program repair which extends the original single objective GenProg by adding additional objectives to satisfy the fitness function. Additionally, to verify if the success of GenProg is indeed due to genetic programming and not mutation/crossover operations, we study to performance of NSGAII~\cite{nsgaii}. It is also worth noting that, to be best of our knowledge, this is the first attempt to study multiobjective patch generation in automated program repair.

@@

\section{Research Questions}
\label{rq}
We conjecture that one way to further the research in the area of automated patch generation may be by modeling the domain as a multiobjective search problem. Consider genetic programming --- the algorithm works by trying to maximize the ``fitness'' score. In this case, the number of passing test cases given a patch. Algorithms like RSRepair, on the other hand, considers either repair effectiveness (as measured by the number patch trials required) or repair efficiency (measured by the number of test case executions). It is not hard to see that each of these objectives namely, the number of passing test cases, the repair effectiveness, and the repair efficiency, are all important. Perhaps some are more important than others, but they all play a crucial role nonetheless.

@@

\subsection*{RQ3: Can we replace genetic programming by some other genetic algorithm?}
\label{rq3}
Assuming that we can answer RQ2, this question would be a natural extension to that. Here we ask what would happen if we used a different multiobjective optimizer in place of genetic programing. With this, we seek to validate (or perhaps deprecate) certain claims of studies by Qi et al.~\cite{qi2014}. They consider that the success of GenProg is due to the mutate operation of evolutionary algorithms and not genetic programming.

@@

We believe this to be untrue and to verify our opinion we replace GP with NSGAII~\cite{nsgaii}. NSGAII is an incredibly popular variant of GA (18000+ citations). It consists of a novel sort algorithm that enables it identify better solutions and to converge at these solution much faster.

@@

This measure is used to study the nature of patches generated by a search algorithm. It is entirely possible that a bug may be fixed in more that one way. Then, an method that can explore a much larger search space would be an enticing alternative to a narrow search scheme.  
\input{figs/results2.tex}
\pagebreak
\section{Experimental Results}
\label{results}

@@

As for future work, efforts must be taken to update the notation of patches prior to performing search. Also, other novel search strategies that use both GP and Non-dominated sort may be explored. In addition to this, the usefulness of a promising new algorithm called SWAY\footnote{This algorithm is in current development by our research group}~\cite{chen2016sampling, nair2016accidental} may be also be investigated.
\balance
\bibliographystyle{unsrt}
\bibliography{references}
\end{document}
